A robust and memory-efficient transition state search method for complex energy landscapes

### 2022-09-01 manuscript.tex
Minor changes

The second system is an elastic cylindrical shell, modelled by a triangulated mesh of nodes, which interact via extensional and angular springs.
The \num{35400} degrees of freedom are the node coordinates in three-dimensional space.
The characteristic transition in \cref{fig:testsystems}b shows the formation of a stable dimple from an initially unbuckled cylinder.
This transition is essential to capture to predict mechanical failure under strain \cite{Panter2019,Virot2017}.
}

@@

\hl{%
The results for the three systems are shown in \cref{tab:speed}.
First, we note that for all three systems, using hybrid eigenvector following does not significantly improve the speed of BITSS.
Indeed, for buckling and especially wetting, HEVF is detrimental to performance.
Next, it is interesting to compare each method's performance between simple and complex pathways.
In contrast to the wetting transition's highly non-linear pathway, the pathways of the LJ-7 rearrangement and the buckling system can be simply tracked following a gradual variation in the order parameters.
For LJ-7, this is the translation of atoms 5 and 6, and for buckling, this is the radial displacement of the centre of the dimple \cite{Panter2019}.
For the simpler pathways, BITSS is generally slower, but for the complex pathways, BITSS is faster.
Moreover, we see that for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.

For situations where memory is limited, it is important to minimise the number of images used.
However, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF if too few images are used, as observed for the cylindrical buckling with three images.
BITSS, on the other hand, converges using only two images.
}

@@

\hl{%
\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
The spring constants used to connect the states in the CINEB and DNEB methods are system dependent.
They are chosen such that they keep the states equidistant without overwhelming the gradients arising from the potential energy landscapes under consideration.
We employ $10^{-1}$ for the Lennard-Jones particle cluster, $10^{-2}$ for the cylindrical buckling example, and $10^{-6}$ for the striped wetting system.

>>>>

The second system is an elastic cylindrical shell, modelled by a triangulated mesh of nodes, which interact via extensional and angular springs.
The \num{35400} degrees of freedom are the node coordinates in three-dimensional space.
The characteristic transition in \cref{fig:testsystems}b shows the formation of a stable dimple from an initially unbuckled cylinder.
This transition is essential to capture and predict mechanical failure under strain \cite{Panter2019,Virot2017}.
}

@@

\hl{%
The results for the three systems are shown in \cref{tab:speed}.
First, we note that for all three systems, using hybrid eigenvector following does not significantly improve the speed of BITSS.
Indeed, for buckling and especially wetting, HEVF is detrimental to performance.
Next, it is interesting to compare each method's performance between simple and complex pathways.
In contrast to the wetting transition's highly non-linear pathway, the pathways of the LJ-7 rearrangement and the buckling system can be simply tracked following a gradual variation in the order parameters.
For LJ-7, this is the translation of atoms 5 and 6, and for buckling, this is the radial displacement of the centre of the dimple \cite{Panter2019}.
For the simpler pathways, BITSS is generally slower, but for the complex pathways, BITSS is faster.
Moreover, we see that for the wetting example, CINEB does not converge to the transition state because the estimated tangent vector is highly inaccurate due to the non-linearity of the pathway.
}

\hl{%
For situations where memory is limited, it is important to minimise the number of images used.
However, efficiently finding the TS is challenging for both CINEB and DNEB-HEVF if too few images are used, as observed for the cylindrical buckling with three images.
BITSS, on the other hand, converges using only two images.
}

@@

\section{Implementation details for the CINEB, DNEB-HEVF, and BITSS-HEVF methods}\label{sec:HEVFdetails}
\hl{%
The spring constants used to connect the states in the CINEB and DNEB methods are system dependent.
They are chosen such that they keep the states equidistant without overwhelming the gradients arising from the potential energy landscapes under consideration.
We employ $10^{-1}$ for the Lennard-Jones particle cluster, $10^{-2}$ for the cylindrical buckling example, and $10^{-6}$ for the striped wetting system.
